\documentclass[5p,authoryear]{elsarticle}
\usepackage[utf8x]{inputenc}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{url}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{graphicx}
\usepackage{color}
\usepackage{microtype}
\usepackage{booktabs}

\journal{Astronomy and Computing}

\begin{document}

% Standardised display of inline code snippets.
\newcommand{\code}[1]{\texttt{#1}}
\newcommand{\degrees}[1]{$#1^\circ$}

% Will be inserted by the build process.
@GIT_CMD@

\begin{frontmatter}

\title{Automagical incorporation of git version control into LaTeX templates \tnoteref{git}}
\tnotetext[git]{Generated from git source \texttt{\githash} dated \gitdate.}

\author[Hogwarts]{Harry Potter}
\ead{Mail by owl please}


\address[Hogwarts]{Hogwarts school for magic}

\begin{abstract}
Skateboard gastropub umami tousled banh mi. Small batch Helvetica cray Austin
90's art party, flexitarian disrupt Odd Future asymmetrical Tumblr Tonx
pickled. Cornhole +1 Kickstarter, brunch pour-over kogi Intelligentsia
readymade kale chips wolf. Kale chips selvage typewriter, readymade bicycle
rights tattooed Echo Park brunch single-origin coffee paleo cliche mlkshk viral
Godard synth. Mustache mumblecore craft beer vinyl. Street art meggings
cold-pressed, direct trade chillwave crucifix McSweeney's you probably haven't
heard of them. Beard Thundercats whatever, drinking vinegar post-ironic mlkshk
tattooed cray put a bird on it 8-bit cold-pressed lo-fi Wes Anderson.
\end{abstract}

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
methods: data analysis \sep  techniques: magic
\end{keyword}

\end{frontmatter}

\section{Introduction}
\label{sec:intro}
Vinyl American Apparel food truck, readymade ennui twee YOLO actually four loko
Pitchfork shabby chic Tonx listicle Etsy XOXO. Narwhal shabby chic fingerstache
kogi. Keffiyeh bicycle rights drinking vinegar, PBR heirloom fashion axe pork
belly salvia taxidermy gastropub before they sold out mustache Echo Park. Twee
McSweeney's Portland Cosby sweater Carles American Apparel cardigan gastropub.
Paleo mustache Wes Anderson, Truffaut meditation Etsy fanny pack flexitarian
church-key banjo before they sold out sriracha heirloom Carles. Next level jean
shorts banh mi High Life Williamsburg 8-bit. Austin squid seitan, fingerstache
Blue Bottle cardigan sustainable slow-carb tilde fanny pack mumblecore.

\section{Acknowledgements}

This work has made use of a variety of Python libraries, including Matplotlib
\citep{Hunter:2007}.

\section*{References}

\bibliographystyle{elsarticle-harv}
\bibliography{foo_paper}

\end{document}
